\documentclass{article}
\usepackage[utf8]{inputenc}
\title{Bibliography}

\begin{document}
\section{History of Radio Control}
	\subsection{About}
	URL: https://rcflightline.com/rc-history/\\
	Author:\\
	Viewed on: 3/20/2017

	\subsection{Summary}
	\begin{enumerate}
	\item First patent for a radio controlled device was issed to
	Nikola Tesla in 1898. He demostrated a remote controlled boat in
	Madison Square Garden, New York, NY.
	\item In the 1920's remote controlled boats were widely used in
	the navies as artillery practice. Later used in aircrafts to
	train pilots, used in the Britain air force.
	\end{enumerate}

	\subsection{Notes}
	Not very good, as sources for this article are either broken, or
	linking to site that does not correspont to any of the information
	mentioned.
	
\section{RC Spread Spectrum Demystified}
	\subsection{About}
	URL: http://www.rchelicopterfun.com/RC-Spread-Spectrum.html \\
	Author: David E. Buxton\\
	Viewed on: 4/2/2017

	\subsection{Summary}
	\begin{enumerate}
	\item Todays RC transmitter and receiver as using 2.4 GHz Spread Spectrum 
	modulation scheme.
	\begin{itemize}
		\item Frequency Hopping Spread Spectrum (FHSS): Transmitter and
		receiver hop in unison to a mutually common pseudo random sequence of
		frequencies. One or more packets of data are transmitted before each
		hop.
		\item Direct Sequence Spread Spectrum (DSSS)CDMA?: Digital sequence
		modulation applied to the carrier frequency. Looks like noise on
		a spectrum analyzer. The recommended form of modulation used by FHSS
		for transmitting data.
		\item Cyclical Redundancy Code (CRC): A key premise is that data
		sometimes gets corrupted. The transmitter’s and receiver’s CRC
		calculation won’t match if even one bit is off. RC receivers ignore
		flawed packet’s, Wi-Fi asks for a retry.
	\end{enumerate}

	\subsection{Notes}
		Great article! Walks through todays radios that are used in RC 
		aircrafts.
\section{The Good old Days – The Birth of RC}
	\subsection{About}
	URL: http://www.modelairplanenews.com/the-first-days-of-rc/ \\
	Author: Gerry Yarrish\\
	Viewed on: 4/3/2017

	\subsection{Summary}

\section{RC Radios For Helicopters & Airplanes}
	\subsection{About}
	URL: http://www.rchelicopterfun.com/rc-radios.html \\
	Author: \\
	Viewed on: 4/3/2017

	\subsection{Summary}

\end{document}